ManuscriptPURFits

### 2024-02-22 Code/ManuscriptPURFits.Rmd
Generated WL ANOVA figure

# # model with dummy dark, 0 PAR,  growth rates 
# PURPARStrainO2WLNestModels <- PURPARFits_dummy |>
#   nest(data = -c("Strain","O2_uM", "WL")) |>
#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
#                               data = .x,
#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
#                               lower = c(0, 0, 0),
#                               upper = c(1,1,100),
#                               control = list(maxiter = 500)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
#          )|>
#   mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
#                               data = .x,
#                               start = LinEqnStart
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRClm_Param = map(GRClm_Model, tidy),
#          GRClm_Predict = map(GRClm_Model, possibly(augment)),
#          GRClm_Glance = map(GRClm_Model, possibly(glance))
#          )
# 
# 
# # model with dummy dark, 0 PAR,  growth rates
# PURPARStrainO2PeriodWLNest <- PURPARFits_dummy |>
#   nest(data = -c("Strain","O2_uM", "Photoperiod", "WL")) |>
#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
#                               data = .x,
#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
#                               lower = c(0, 0, 0),
#                               upper = c(1,1,100),
#                               control = list(maxiter = 500)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
#          )|>
#   mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
#                               data = .x,
#                               start = LinEqnStart
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRClm_Param = map(GRClm_Model, tidy),
#          GRClm_Predict = map(GRClm_Model, possibly(augment)),
#          GRClm_Glance = map(GRClm_Model, possibly(glance))
#          )
remove(AllData)

@@

@@

ANOVA_AllPhotoperiods <- AllFitsCombined %>% 
  mutate(twelve = `Model_12`,
         four = `Model_4`,
         eight = `Model_8`,
         sixteen = `Model_16`) %>%
  mutate(fourvsAll = map(map2(four, All, possibly(anova, otherwise = NULL)), tidy),
         eightvsAll = map(map2(eight, All, possibly(anova, otherwise = NULL)), tidy),
         twelvevsAll = map(map2(twelve, All, possibly(anova, otherwise = NULL)), tidy),
         sixteenvsAll = map(map2(sixteen, All, possibly(anova, otherwise = NULL)), tidy)) %>% 
  select(Strain, O2_uM, fourvsAll, eightvsAll, twelvevsAll, sixteenvsAll) %>% 
  pivot_longer(cols = c(fourvsAll, eightvsAll, twelvevsAll, sixteenvsAll)) %>% 
  unnest(value, keep_empty = TRUE) %>% 
  filter(is.na(term) & is.na(p.value) |
           !is.na(term) & !is.na(p.value)) %>%
  select(Strain, O2_uM, name, p.value) %>% 
  separate(name, into = c("Photoperiod1", "AllPhotoperiod"), sep = "vs") %>% 
  mutate(pvalue = signif(`p.value`, digits = 2))

@@

# Fits are added that are not sig different individually,  next add fits that were sig different dynamically
```{r Plot fits, fig.height= 20, fig.width= 20 }

@@

```{r Pur plot strain facetted in columns}
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }

@@

@@

   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM == 25, Strain == "MIT9313")) +

@@

>>>>

# model with dummy dark, 0 PAR,  growth rates
PURPARStrainO2WLNestModels <- PURPARFits_dummy |>
  nest(data = -c("Strain","O2_uM", "WL")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1),
                              lower = c(0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )|>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

# 
# # model with dummy dark, 0 PAR,  growth rates
# PURPARStrainO2PeriodWLNest <- PURPARFits_dummy |>
#   nest(data = -c("Strain","O2_uM", "Photoperiod", "WL")) |>
#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
#                               data = .x,
#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
#                               lower = c(0, 0, 0),
#                               upper = c(1,1,100),
#                               control = list(maxiter = 500)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
#          )|>
#   mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
#                               data = .x,
#                               start = LinEqnStart
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRClm_Param = map(GRClm_Model, tidy),
#          GRClm_Predict = map(GRClm_Model, possibly(augment)),
#          GRClm_Glance = map(GRClm_Model, possibly(glance))
#          )
remove(AllData)

@@

PURPARStrainO2WLNestModels|>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
   scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2_uM, WL), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2WLNestModels Linear Model") +
  theme_bw()

PURPARStrainO2WLNestModels|>
  filter(!map_lgl(GRClm_Model, is.null)) |>
  unnest(GRClm_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
   scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2_uM, WL), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2WLNestModels Linear Model") +
  theme_bw()

@@

ANOVA_AllPhotoperiods <- AllFitsCombined %>% 
  mutate(twelve = `Model_12`,
         four = `Model_4`,
         eight = `Model_8`,
         sixteen = `Model_16`) %>%
  mutate(fourvsAll = map(map2(four, All, possibly(anova, otherwise = NULL)), tidy),
         eightvsAll = map(map2(eight, All, possibly(anova, otherwise = NA)), tidy),
         twelvevsAll = map(map2(twelve, All, possibly(anova, otherwise = NULL)), tidy),
         sixteenvsAll = map(map2(sixteen, All, possibly(anova, otherwise = NULL)), tidy)) %>% 
  select(Strain, O2_uM, fourvsAll, eightvsAll, twelvevsAll, sixteenvsAll) %>% 
  pivot_longer(cols = c(fourvsAll, eightvsAll, twelvevsAll, sixteenvsAll)) %>% 
  unnest(value, keep_empty = TRUE) %>% 
  filter(is.na(term) & is.na(p.value) |
           !is.na(term) & !is.na(p.value) | is.nan(p.value)) %>%
  select(Strain, O2_uM, name, p.value) %>% 
  separate(name, into = c("Photoperiod1", "AllPhotoperiod"), sep = "vs") %>% 
  mutate(pvalue = signif(`p.value`, digits = 2))

@@

```{r PhotoperiodAnovaTable, include = FALSE}

PhotoperiodAnovaTable <- ANOVA_AllPhotoperiods %>% 
  mutate(Photoperiod = as.numeric(case_when(Photoperiod1 == 'four' ~ 4,
                                  Photoperiod1 == 'eight' ~ 8,
                                  Photoperiod1 == 'twelve' ~ 12,
                                  Photoperiod1 == 'sixteen' ~ 16)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) %>% 
  select(-c(Photoperiod1, p.value, AllPhotoperiod))  %>%
  relocate(Photoperiod, .after = O2_uM) %>%
  arrange(Strain, O2_uM,Photoperiod)

```{r PhotoperiodAnovaTable, fig.height = 6, fig.width = 8, echo = FALSE }

knitr::kable(PhotoperiodAnovaTable,
             caption = "pvalues for each photoperiod from ANOVA comparison with a fit of pooled photoperiods in each O~2~ experiment for each strain.",
            col.names =  c("Strain",
                           "[O~2~] (µM)",
                          "Photoperiod (h)",
                          "pvalue"),
              align = "lccc"
             )
```

# This figure is a 3 panel figure faceted by strain in columns and O2 in rows. Too stretched.
# Fits are added that are not sig different individually,  next add fits that were sig different dynamically
```{r Plot fits, fig.height= 20, fig.width= 20 }

@@

```{r Pur plot strain faceted in columns}
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }

@@

   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotdash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "SS120")) +

@@

   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 25, Strain == "MIT9313")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +

@@

# WL models for each strain for each O2 experiment
```{r Generate platt and lm for WL}

# model with dummy dark, 0 PAR,  growth rates. Also removed data if no growth occurred for an O2 and photoperiod combination so that the model including all photoperiods would not be skewed towards zero.
StrainO2NestModels <- PURPARFits_dummy |>
  nest(data = -c("Strain","O2_uM")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
                              lower = c(0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

StrainO2NestModels <- full_join(StrainO2NestModels, AllData)

# model with dummy dark, 0 PAR,  growth rates
PURPARStrainO2WLNestModels <- PURPARFits_dummy |>
  nest(data = -c("Strain","O2_uM", "WL")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1),
                              lower = c(0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )|>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

remove(AllData)

# Want platt model for all fits that did not fail and lm for platt models that returned a NULL
```{r models for WL}
# O2 and WL nested data frame containing the fits for each WL for each strain
#filter to keep platt models
KeepPlattModel <- PURPARStrainO2WLNestModels|>
  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
   filter(!map_lgl(GRCplatt_Model, is.null))

#filter to keep only the models that failed to fit a platt model, fits by lm remains. 
KeepLmModel <- PURPARStrainO2WLNestModels|>
  filter(map_lgl(GRCplatt_Model, is.null)) |>
 select(-c(GRCplatt_Glance, GRCplatt_Model, GRCplatt_Param, GRCplatt_Predict))

# Join  
StrainO2WL_AllModels <- bind_rows(KeepPlattModel, KeepLmModel)

# O2 and WL nested data frame containing the fits for each WL for each strain
 StrainO2WL_PlattLmModel <- StrainO2WL_AllModels |>
   pivot_longer(cols = -c(Strain, O2_uM, WL, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param") | str_detect(name, pattern = "Predict")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
filter(!map_lgl(Model, is.null)) |>
  filter(!map_lgl(Glance, is.null)) |>
  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
  group_by(Strain, O2_uM, WL) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
  select(-c(Glance)) |>
  unnest(Param) |>
  select(-c(statistic)) |>
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))

# O2 nested data frame containing the single fit of pooled WL
 #filter to keep platt models
KeepPlattModel <- StrainO2NestModels|>
  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
   filter(!map_lgl(GRCplatt_Model, is.null))

#filter to keep only the models that failed to fit a platt model, fits by lm remains. 
KeepLmModel <- StrainO2NestModels|>
  filter(map_lgl(GRCplatt_Model, is.null)) |>
 select(-c(GRCplatt_Glance, GRCplatt_Model, GRCplatt_Param, GRCplatt_Predict))

# O2 nested data frame containing the single fit of pooled WLs 
 StrainO2_PlattLmModel <- StrainO2_AllModels|>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, data, Data_all)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param") | str_detect(name, pattern = "Predict")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
  filter(!map_lgl(Model, is.null)) |>
  filter(!map_lgl(Glance, is.null)) |>
  mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
  group_by(Strain, O2_uM) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
  select(-c(Glance))|>
  unnest(Param) |>
  select(-c(statistic)) |>
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))

 remove(KeepPlattModel)
 remove(KeepLmModel)
 # remove(StrainO2WL_AllModels)
 # remove(StrainO2_AllModels)

# O2 nested data frame containing the single fit of pooled photoperiods for each strain 
StrainO2_PlattLmModel <- StrainO2_PlattLmModel|>
  mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
         estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
         estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
         AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC))

StrainO2_PlattLmModel

# O2 and Photoperiod nested data frame containing the fits for each photoperiod for each strain
StrainO2WL_PlattLmModel <- StrainO2WL_PlattLmModel|>
  mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
         estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
         estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
         AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC))

StrainO2WL_PlattLmModel

```{r plot WL models}

# O2 nested data frame containing the single fit of pooled photoperiods for each strain
StrainO2_PlattLmModel |>
  unnest(Predict, data) |>
  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         WL= factor(WL, levels = c("WW", 660, 450)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4"))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL))) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
   geom_text(aes(x = 500000, y = 0.75, label = paste(ModelType), show.legend = FALSE)
  ) +
     scale_colour_manual(values = MCMIXColours) +
   scale_shape_manual(values = PhotoperiodShapes)  +
  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
    labs(title = "Single fit for each strain in each [O2]- all WL ") +
  theme_bw()

# O2 and Photoperiod nested data frame containing the fits for each photoperiod for each strain
StrainO2WL_PlattLmModel |>
  unnest(Predict, data) |>
  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
   geom_text(aes(x = 500000, y = 0.75, label = paste(ModelType), show.legend = FALSE)
  ) +
     scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2_uM, WL), cols = vars(Strain)) +
    labs(title = "Fits to be used for ANOVA comparison to single fit across each strain and [O2]") +
  theme_bw()

# ANOVA comparison of red light to blue light for each strain and [O2]. 
```{r compare 1 red and blue light fits}

# make wider to join with DF that contains the 1 fit through all photoperiods
Wider_WL <- StrainO2WL_PlattLmModel %>% 
  select(Strain, WL, O2_uM, Model, Predict) %>% 
  pivot_wider(names_from = WL, values_from = c(Model, Predict))

# this contains 1 fit through all WL.
AllWL <- StrainO2_PlattLmModel %>% 
  select(Strain, O2_uM, Model, Predict, Data_all) %>% 
 rename(All = 'Model',
        Predict_pooled = 'Predict')

AllFitsCombinedWL <- left_join(Wider_WL, AllWL)

ANOVA_AllWL <- AllFitsCombinedWL %>% 
  mutate(Blue = `Model_450`,
         Red = `Model_660`,
         White = `Model_WW`,
         Pooled = `All`) %>%
  mutate(BluevsPooled = map(map2(Blue, Pooled, possibly(anova, otherwise = NULL)), tidy),
         RedvsPooled = map(map2(Red, Pooled, possibly(anova, otherwise = NA)), tidy),
         WhitevsPooled = map(map2(White, Pooled, possibly(anova, otherwise = NULL)), tidy),
         BluevsRed = map(map2(Blue, Red, possibly(anova, otherwise = NULL)), tidy)) %>% 
  select(Strain, O2_uM, BluevsPooled, RedvsPooled, WhitevsPooled, BluevsRed) %>% 
  pivot_longer(cols = c(BluevsPooled, RedvsPooled, WhitevsPooled, BluevsRed)) %>% 
  unnest(value, keep_empty = TRUE) %>% 
  filter(is.na(term) & is.na(p.value) |
           !is.na(term) & !is.na(p.value) | is.nan(p.value)) %>%
  select(Strain, O2_uM, name, p.value) %>% 
  separate(name, into = c("WL1", "WL2"), sep = "vs") %>% 
  mutate(pvalue = signif(`p.value`, digits = 2))

ANOVA_AllWL %>% 
  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
    # mutate(Photoperiod1 = factor(Photoperiod1, levels = c('four','eight', 'twelve', 'sixteen'))) %>% 
  ggplot() +
  geom_text(aes(x = WL1, y = WL2, label = pvalue), data = . %>% filter(pvalue < 0.05), size = 2.5) +
  geom_text(aes(x = WL1, y = WL2), data = . %>% filter(pvalue > 0.05), label = "ns") +
  geom_text(aes(x = WL1, y = WL2), data = . %>% filter(is.na(pvalue)), label = "NA") +
  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
  labs(title = "ANOVA compare all models",
       caption = "NA = atleast one model did not fit due to lack of data points; 
       ns = not significantly different from WL model (p value > 0.05); 
       numbers = significantly different pvalues from all WL model (p value < 0.05)")

remove(Wider_WL)
remove(AllWL)

```{r Pur plot strain faceted in columns}
scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }

WLvsPooledPurFitsPlots <- AllFitsCombinedWL |>
  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.7) +
    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.0, alpha = 0.5) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_450) %>%  filter(O2_uM == 2.5, Strain == "MED4",  WL == 450)) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MED4", WL == 660))+
    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MED4", WL == "WW")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 450)) +
 geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "SS120", O2_uM != 250, WL == "WW")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 660))+
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MIT9313", O2_uM == 2.5, WL == "WW")) +
 labs(title = "Anova fit comparisons of WL to pooled", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +

WLvsPooledPurFitsPlots

# This labels each pane with a letter but turns of the facet labels
# AllStrainPurFitsPlots <- tag_facet(AllStrainPurFitsPlots, open = "", close = "", tag_pool = LETTERS, size = 8)

BluevsRedPurFitsPlots <- AllFitsCombinedWL |>
  filter(Data_all_WL %in% c(450,660)) %>% 
         WL = factor(Data_all_WL, levels = c(660, 450)),
  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.7) +
    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.0, alpha = 0.5) +
 #  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_450) %>%  filter(Strain == "MED4",  WL == 450)) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MED4", WL == 660)) +
 #    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MED4", WL == "WW")) +
 #   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 450)) +
 geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_660) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 660)) +
   # geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 660))+
    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_450) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 450))+
 #  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MIT9313", O2_uM == 2.5, WL == "WW")) +
 labs(title = "Sig diff fits are indicated by the fit drawn. No lines, no diff bt 660 & 450", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +

BluevsRedPurFitsPlots
